Forecasting the 2024 U.S. Presidential Election: Kamala Harris' Projected Victory

### 2024-11-03 paper/paper.qmd
committing changes in model section to paper.qmd

The paper focuses on Donald Trump and Kamala Harris, the two leading candidates in the current presidential election race. For all the following variables mentioned, we collected observations for both of the candidates. We collect observations from the dataset where the ‘candidate_name’ is Trump and Harris. We are interested in the support for both candidates over time, for each state, therefore, we collect observations of ‘end_date’, and ‘state’, as well as the electorate support for each candidate is denoted as ‘pct’. Furthermore, since there are many pollsters present in the dataset, we extracted pollsters with high-quality data that is reliable, which is denoted as having a high ‘numeric_grade’ and ‘transparency_score’, details of data cleaning are further explained in {additional data details}.

@@

- \( P(\text{Victory}_i) \) is the predicted probability of winning for candidate \( i \).
- \( \beta_0 \) represents the intercept, reflecting the baseline log-odds of winning.
- \( \beta_1 \) is the coefficient for the natural spline transformation of the numeric end date \( (\text{end\_date\_num}_i) \), capturing nonlinear trends in voter support over time.
- \( u_{\text{state}} \) is the random effect associated with each state, accounting for variations in voter preferences.

@@

- \(y_i\) represents the proportion of support for candidate \(i\) in a given state.
- \(\mu_i\) is the mean of the Beta distribution, reflecting the expected support proportion.
- \(\phi\) is the precision parameter, indicating the variability around the mean.

>>>>

The present analysis focuses on Donald Trump and Kamala Harris, the two leading candidates in the current presidential election race. For all the following variables mentioned, we collected observations for both of the candidates. We collect observations from the dataset where the ‘candidate_name’ is Trump and Harris. We are interested in the support for both candidates over time, for each state, therefore, we collect observations of ‘end_date’, and ‘state’, as well as the electorate support for each candidate is denoted as ‘pct’. Furthermore, since there are many pollsters present in the dataset, we extracted pollsters with high-quality data that is reliable, which is denoted as having a high ‘numeric_grade’ and ‘transparency_score’, details of data cleaning are further explained in [@sec-data-details]

@@

- $P(\text{Victory}_i)$ is the predicted probability of winning for candidate $i$.
- $\beta_0$ represents the intercept, reflecting the baseline log-odds of winning.
- $\beta_1$ is the coefficient for the natural spline transformation of the numeric end date $(\text{end\_date\_num}_i)$, capturing nonlinear trends in voter support over time.
- $u_{\text{state}}$ is the random effect associated with each state, accounting for variations in voter preferences.

@@

- $y_i$ represents the proportion of support for candidate $i$ in a given state.
- $\mu_i$ is the mean of the Beta distribution, reflecting the expected support proportion.
- $\phi$ is the precision parameter, indicating the variability around the mean.
